---
title: "Assig 04-AMM"
author: "Chathurani Ekanayake"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**import required packages**
```{r}
#install.packages("Benchmarking")
library(Benchmarking)
```


```{r}
if(!require(knitr)){
  library(knitr)
}
```

```{r}
library(kableExtra)
```

# Data 
```{r}
df <- data.frame(
  DMU = c("Facility 1", "Facility 2", "Facility 3", "Facility 4", "Facility 5", "Facility 6" ), 
  Staff_hours_per_day = c(100,300,320,500,350,340), 
  Supplies_per_day = c(0.3,0.6,1.2,2,1.4,0.7),
  Reimbursed_patient_days = c(15000,15000,40000,28000,20000,14000),
  Privetly_paid_patient_days = c(3500,20000,11000,42000,25000,15000)
)
 
```


```{r}
kable(df,format = "pandoc",caption = "Hope Valley Health Care Association")
```

**create the matrix with given data**
 
 x- contains input data (Supplies per day,Staff hours per day)
 y- contains output data (Reimbursed patient days, Privetly paid patient days)

```{r}
x <- matrix(c(100,300,320,500,350,340, 
             0.3,0.6,1.2,2,1.4,0.7), ncol = 2)
y <- matrix(c(15000,15000,40000,28000,20000,14000, 
              3500,20000,11000,42000,25000,15000), ncol = 2)
colnames(x) <- c("Supplies_per_day","Staff_hours_per_day")
colnames(y) <- c("Reimbursed_patient_days", "Privetly_paid_patient_days") 
```

**Questions**
1. Formulate and perform DEA analysis under all DEA assumptions of FDH, CRS, VRS,
IRS, DRS, and FRH.
2. Determine the Peers and Lambdas under each of the above assumptions
3. Summarize your results in a tabular format
4. Compare and contrast the above result

# DEA Analysis using FDH

Now, we are going to formulate and compute the DEA analysis under the assumption of FDH. The Free Disposability Hull (FDH) is a way to measure how efficient a company is at producing outputs with its inputs. It assumes that a company can always get rid of unwanted inputs and outputs without cost.

**input and output values**
```{r}
fdh <- dea(x,y,RTS = "fdh")
```

**calculate efficiency and name the column**

```{r}
eff_fdh <- as.data.frame(fdh$eff)
colnames(eff_fdh)<- c("efficiency_fdh")
eff_fdh
```
According to the above results, under the FDH assumption, Facilities 1 to 5 are operating at full efficiency, while Facility 6 is slightly less efficient (0.8823529)  in its resource utilization. An efficiency score of 1.0000000 represents full efficiency, and scores lower than 1 indicate some level of inefficiency. Facility 6 has room for improvement in its input-output efficiency compared to the other facilities. 

In the case of the sixth nursing home, it is possible that the nursing home could reduce its staffing hours or the cost of supplies without sacrificing quality. For example, the nursing home could implement new efficiency measures or negotiate better prices with suppliers.

**Find the peers** 
```{r}
peer_fdh<-peers(fdh)
colnames(peer_fdh)<- c("peer_fdh")
peer_fdh
```
According to the results of peer column, Facility 1 is compared to Facility 1 itself, and its peer index is 1.
Facility 2 is compared to Facility 2 itself, and its peer index is 2.
Facility 3 is compared to Facility 3 itself, and its peer index is 3.
Facility 4 is compared to Facility 4 itself, and its peer index is 4.
Facility 5 is compared to Facility 5 itself, and its peer index is 5.
Facility 6 is compared to Facility 2, and its peer index is 2.
The peer index of 1 for Facilities 1, 2, 3, 4, and 5 means that they are considered efficient (i.e., they are their own peers), while Facility 6 is compared to Facility 2 as its peer. Facility 6 may not be as efficient as the others, as it's not considered its own peer under the FDH assumption.


**Find the lambda**
```{r}
lambda_fdh <- lambda(fdh)
lambda_fdh
```
According to the above results, L1, L2, L3, L4, L5: These columns represent the facilities (Facility 1 to Facility 5) that serve as peers for each of the six facilities, including Facility 6.

Facility 1,2,3,4 and 5 are 100% efficient, and its efficiency score is calculated by comparing it to itself.Facility 6 is less efficient than the other facilities, and its efficiency score is calculated by comparing it to Facility 2. This means that Facility 6 could improve its efficiency by using its inputs and outputs more efficiently, or by finding ways to reduce its inputs or increase its outputs.

**Tabular data for FDH**
```{r}
tabular_fdh <- cbind(peer_fdh,lambda_fdh,eff_fdh)
tabular_fdh
```
**Interpretation of lambda**

Lambda values in DEA indicate how much a DMU (Decision Making Unit) borrows or learns from its efficient peers. Larger lambda values mean a DMU learns more from its peers to become efficient.According to the tabular data, only facility 6 is inefficient. So inefficiency of \($$DMU_6$$ = 1 - 0.88 = 0.12\). \($$DMU_6$$\) can reduce this 12% inefficiency learning from its peer of \($$DMU_2$$\). 


**Plot the result**

```{r}
dea.plot(x,y,RTS = "fdh", ORIENTATION = "in-out", txt = TRUE, main= "Free Disposability Hull (FDH) Graph")
```

# DEA Analysis using CRS 
Now, we will formulate and compute the DEA analysis using the Constant Returns to Scale (CRS) assumption. CRS is a part of the scaling assumption, and it helps us determine if there are any feasible combinations for scaling up or down, without changing the overall efficiency

**input and output values** 
```{r}
crs <- dea(x,y,RTS = "crs")
```

**calculate efficiency and name the column**
```{r}
eff_crs <- as.data.frame(crs$eff)
colnames(eff_crs)<- c("efficiency_crs")
eff_crs
```
As per the above results, Facility 1, 2 and 4 are operating at optimal efficiency under the CRS assumption. Facilities 3, 5, and 6 have room for improvement in their resource utilization and output generation. You can use these efficiency scores to rank and compare the facilities in terms of their efficiency and identify which ones have the most significant efficiency gaps.


**Find the peers** 
```{r}
peer_crs<-peers(crs)
peer_crs
```
The above matrix represent potential peers for each of the six entities (or DMUs). DMU1,DMU2 and DMU4 are their own peers.Therefore those three DMUs can be considered as efficient. DMU3 and 5 have two peers for each of them,DMU1 and DMU4. DMU6 also has two peers, DMU1 and DMU2.Due to those three DMUs (DMU3,5 and 6) have two peers those are considered as inefficient. 

**Find the lambda**
```{r}
lambda_crs <- lambda(crs)
lambda_crs
```
Rows 1 to 6 correspond to Facilities 1 to 6.

Column "L1" represents the lambda value for Facility 1. It is 1.0000000, indicating that Facility 1 can achieve efficiency by itself (it doesn't need to rely on other facilities).

Column "L2" represents the lambda value for Facility 2. Similar to Facility 1, it is 1.0000000, indicating that Facility 2 is also efficient on its own.

Column "L4" represents the lambda value for Facility 4. It is 1.0000000, indicating that Facility 4 can achieve efficiency independently.

For the other facilities (Facilities 3, 5, and 6):

Facility 3 has a lambda value of 2.5789474 for "L1" and 0.04699248 for "L4." This means that Facility 3 can achieve efficiency by a combination of itself (2.5789474 times) and Facility 1, as well as to a lesser extent by itself and Facility 4 (0.04699248 times).

Facility 5 has a lambda value of 0.2631579 for "L1" and 0.57330827 for "L4." Facility 5 can achieve efficiency by combining itself and Facility 1 (0.2631579 times) and itself and Facility 4 (0.57330827 times).

Facility 6 has a lambda value of 0.2222222 for "L1" and 0.7111111 for "L2." Facility 6 can achieve efficiency by combining itself and Facility 1 (0.2222222 times) and itself and Facility 2 (0.7111111 times).


**Tabular data for CRS**
```{r}
tabular_crs <- cbind(peer_crs,lambda_crs,eff_crs)
tabular_crs
```
According to the tabular data of CRS, \(DMU_3\) is learns from its peers, \(DMU_1(L1)\) and \(DMU_4(L4)\). The lambda value of (L1) and (L4) in this row indicate the degree to which \(DMU_3\) learns from its peers.  The maximum of this inefficiency of \(DMU_3\) can learn from its peer \(DMU_2\) because it's lambda value is more than 1. (it is 2.5789474) and the rest of the inefficiency can learn from \(DMU_4\).

As in the above,for \(DMU_5)\) also inefficient and it is  1-(0.2631579+0.57330827)=0.16353383) So  \(DMU_5\) can reduce this 16.35% inefficiency learning from its peers \(DMU_1(L1)\) and \(DMU_4(L4)\). The ratio of \(DMU_1(L1)\) to \(DMU_4(L4)\) is 4:5. Hence that \(DMU_5\) can learn  0.1058002*(4/9)=0.047022311= 4.7% from peer \(DMU_1\) and 0.1058002*(5/9)=0.058777889=5.88%$  from peer \(DMU_4\).  

As well as \(DMU_6\) is inefficient by 1-(0.2222222+0.7111111)= 0.0666667= 6.67%. \(DMU_6\) can reduce this inefficiency learning from its peers \(DMU_1(L1)\) and \(DMU_2(L2)\).The ratio of \(DMU_1(L1)\) to \(DMU_2(L2)\) is 14:15. So \(DMU_6\) learns 0.0666667
*(14/29)=0.032183924= 3.22% from peer \(DMU_1(L1)\) and 0.0666667 *(15/29)=0.034482776=3.45% from peer \(DMU_2(L2)\). 

All the other facilities, \(DMU_1,DMU_2\) and \(DMU_4\) are operated in full their full efficiency of 1.0000.


**Plot the result**
```{r}
dea.plot(x,y,RTS = "crs", ORIENTATION = "in-out", txt = TRUE, main= "Constant Returns to Scale (CRS) Graph")
```
# DEA Analysis using VRS

We will now conduct a DEA analysis with Variable Returns to Scale (VRS). VRS, a key element of the scaling assumption, enables us to assess the efficiency of operations when changes in inputs and outputs are not proportionate. 

**input and output values** 
```{r}
vrs <- dea(x,y,RTS = "vrs")
```

**calculate efficiency and name the column**
```{r}
eff_vrs <- as.data.frame(vrs$eff)
colnames(eff_vrs)<- c("efficiency_vrs")
eff_vrs
```
Facilities 1, 2, 3, and 4 all have an efficiency score of 1.000, meaning they are efficient under the VRS assumption. These facilities are getting the most out of their inputs, given their specific circumstances.
Facility 5 has an efficiency score of approximately 0.924. This suggests that it is somewhat less efficient than the fully efficient facilities. It may have room for improvement in resource utilization.
Facility 6 has an efficiency score of approximately 0.727. This facility is the least efficient among the group, indicating that it may need significant improvements in resource allocation and management.


**Find the peers**
```{r}
peer_vrs<-peers(vrs)
peer_vrs
```
facility 1,2,3 and 4 are their own peers and no any secondary peer. But for facility 5 has two peers, facility 1 and 4.For facility 6 also has two peers as facility 1 and facility 2.  


**Find the lambda**
```{r}
lambda_vrs <- lambda(vrs)
lambda_vrs
```
As per the above table Facility 1,2,3 and 4 are efficient and indicate the efficiency as 1.000. But Facility 5 is efficient with a weight of 0.4415584. It relies on Facility 1 to achieve efficiency and weight of 0.5584416 and it relies on Facility 4 to achieve efficiency.

Facility 6 is efficient with a weight of 0.3030303. It relies on Facility 1 to achieve efficiency and it is efficient with a weight of 0.6969697. It relies on Facility 2 to achieve efficiency.

**Tabular data for VRS**
```{r}
tabular_vrs <- cbind(peer_vrs,lambda_vrs,eff_vrs)
tabular_vrs
```
As per the above tabular data, \(DMU_1,DMU_2,DMU_3,DMU_4\) are identified as efficient. \(DMU_5\) is inefficient and it is 1-(0.44	+0.55)= 0.01. But \(DMU_5\) can reduce this 1% inefficiency learning from its peers \(DMU_1(L1)\) and \(DMU_4(L4)\).The ratio of \(DMU_1(L1)\) to \(DMU_4(L4)\) is 4:5. Therefore, \(DMU_5\) can learn 0.01*(4/9)=0.004444444= 0.4% from its peer \(DMU_1\)  and 0.01*(5/9)= 0.005555556= 0.56% from its peer \(DMU_4\).

Not only that, \(DMU_6)\) also inefficient by 1-(0.3+0.69)=0.01. This inefficiency can reduce from learning its peers of \(DMU_1(L1)\) to \(DMU_2(L2)\).The ratio between those peers is 14:15. Hence that \(DMU_6) can learn 0.01*(14/29)=0.004827586=0.48% from peer \(DMU_1(L1)\) and 0.01*(15/29)=0.0052= 0.52% from peer \(DMU_2(L2)\).


**Plot the result**
```{r}
dea.plot(x,y,RTS = "vrs", ORIENTATION = "in-out", txt = TRUE, main= "Variable Returns to Scale (VRS) Graph")
```
# DEA Analysis using IRS

We will now perform a DEA analysis under Increasing Returns to Scale (IRS) to determine if scaling up operations is feasible.

**input and output values**
```{r}
irs <- dea(x,y,RTS = "irs")
```

**calculate efficiency and name the column**
```{r}
eff_irs <- as.data.frame(irs$eff)
colnames(eff_irs)<- c("efficiency_irs")
eff_irs
```
According to the above results, under the IRS assumption Facility1,2 and 4 are identified in their full efficiency. But Facility4, 5 and 6 are not full efficient and their efficient score is below 1.


**Find the peers**
```{r}
peer_irs<-peers(irs)
peer_irs
```
According to the above table results, \(DMU_1,DMU_2\) and \(DMU_4\) don't have other peers and they  have become their own peers. So they can be identified as in their full efficiency. But \(DMU_3\) and \(DMU_5\)  have 2 peers for each of them, peer\(DMU_1\) and  peer\(DMU_4\).\(DMU_6\) also have two peers \(DMU_1\) and \(DMU_2\).

**Find the lambda**

```{r}
lambda_irs <- lambda(irs)
lambda_irs
```
These lambda values represent the efficiency scores for each facility:

Facility 1: L1 = 1.000 (Fully efficient under IRS)
Facility 2: L2 = 1.000 (Fully efficient under IRS)
Facility 3: L1 = 2.579, L4 = 0.047 (Inefficient under IRS, but it can improve by reallocating resources)
Facility 4: L4 = 1.000 (Fully efficient under IRS)
Facility 5: L1 = 0.442, L4 = 0.558 (Inefficient under IRS, and it needs to improve resource allocation)
Facility 6: L1 = 0.303, L2 = 0.697 (Inefficient under IRS, and it needs to improve resource allocation)

**Tabular data for IRS**
```{r}
tabular_irs <- cbind(peer_irs,lambda_irs,eff_irs)
tabular_irs
```
As per the above tabular data of IRS, \(DMU_1,DMU_2, DMU_4\) are identified as efficient. \(DMU_3\) is inefficient and it can reduce the inefficiency learning the majority from peer \(DMU_1\) because its' lambda value is higher than 1. As well as the rest of the inefficiency can lean from its' other peer \(DMU_4\).

\(DMU_5\) also inefficient and it is 1-(0.44+0.55)=0.01. \(DMU_1(L1)\) and \(DMU_4(L4)\) are the peers of \(DMU_5\). The ratio between those peers is 4:5. So \(DMU_5\) can learn 0.01*(4/9)= 0.0044=0.44% from peer \(DMU_1(L1)\) and 0.01*(5/9)= 0.005555556= 0.56% from peer \(DMU_4(L4)\).

The \(DMU_6\) also inefficient. It is 1-(0.3+0.69) = 0.01. Although it is inefficient it can learn from its peers of \(DMU_1(L1)\) and \(DMU_2(L2)\). The ratio between the peer L1 and L2 is 14:15. So \(DMU_6\) can learn 0.01*(14/29)=0.004827586
=0.48% from peer \(DMU_1(L1)\) and  0.01*(15/29)=0.005172414= 0.52% from peer \(DMU_2(L2)\).


**Plot the result**
```{r}
dea.plot(x,y,RTS = "irs", ORIENTATION = "in-out", txt = TRUE, main= "Increasing Returns to Scale (IRS) Graph")
```

# DEA Analysis using DRS
We will now conduct a DEA analysis with Decreasing Returns to Scale (DRS), which examines the potential for reducing the scale of operations in various production processes, in contrast to IRS. 

**input and output values**
```{r}
drs <- dea(x,y,RTS = "drs")
```

**calculate efficiency and name the column**
```{r}
eff_drs <- as.data.frame(drs$eff)
colnames(eff_drs)<- c("efficiency_drs")
eff_drs
```
According to the above table results, \(DMU_1,DMU_2,DMU_3,DMU_4\) are in their full efficiency. Due to \(DMU_5\) and \(DMU_6\) efficiencies are below 1, those two identified as inefficient DMUs under the DRS assumption.  

**Find the peers**
```{r}
peer_drs<-peers(drs)
peer_drs
```
According to the above matrix, Facility1,facility2, facility3 and facility 4 become their own peers and they don't have any other peers. So those 4 DMUs are efficient. But \(Dmu_5\) has two peers \(DMU_1\) and and \(DMU_4\). As well as \(DMU_6\) has two peers as \(DMU_1\) and \(DMU_2\). Therefore \(DMU_5\) and \(DMU_6\) are inefficient.

**Find the lambda**
```{r}
lambda_drs <- lambda(drs)
lambda_drs
```
According to the above lambda values facility1, facility 2, facility 3 and facility 4 are in their full efficiency and they are indicating by the lambda value of 1.Row 5: This row represents the transformation of the data. It indicates that the first dimension (L1) is transformed with a lambda value of approximately 0.2631579, and the fourth dimension (L4) is transformed with a lambda value of approximately 0.5733083.

Row 6: Similarly, this row represents a transformation where the first dimension (L1) is transformed with a lambda value of approximately 0.2222222, and the second dimension (L2) is transformed with a lambda value of approximately 0.7111111. So Facility 5 and 6 are inefficient.  

**Tabular data for DRS**
```{r}
tabular_drs <- cbind(peer_drs,lambda_drs,eff_drs)
tabular_drs
```
As per the above tabular data of DRS, \(DMU_1,DMU_2,DMU_3, DMU_4\) are identified as efficient. \(DMU_5\) is inefficient and it is 1-(0.2631579+0.5733083)=0.1635338= 16.35% . But \(DMU_5\) can reduce this 16.35% inefficiency learning from its peers \(DMU_1(L1)\) and \(DMU_4(L4)\).The ratio of \(DMU_1(L1)\) to \(DMU_4(L4)\) is 14:15. Therefore, \(DMU_5\) can learn 0.1635338*(14/29)=0.078947352 = 7.89% from peer \(DMU_1(L1)\)  and 0.1635338*(15/29)= 0.084586448=8.46%. from peer \(DMU_4(L4)\). 

On the other hand, \(DMU_6\)also inefficient and it is 1- (0.2222222+0.7111111)=0.0666667=6.67%.  But \(DMU_6\) can reduce its'  inefficiency learning from its peers \(DMU_1(L1)\) and \(DMU_2(L2)\). the ratio between \(DMU_1(L1)\) and \(DMU_2(L2)\) is 14:15 So \(DMU_6\) can learn 0.0666667*(14/29)= 0.032183924 from peer \(DMU_1(L1)\) and 0.0666667*(15/29)= 0.034482776 from peer \(DMU_1(L1)\). 

**Plot the result**
```{r}
dea.plot(x,y,RTS = "drs", ORIENTATION = "in-out", txt = TRUE, main= "Decreasing Returns to Scale (DRS) Graph")
```

# DEA Analysis using FRH

We will now perform a DEA analysis using the Free Replicability Hull (FRH). Like FDH, FRH also utilizes mixed integer programming, where variables are treated as integers to find optimal solutions. FRH aims to replace deterministic data with random variables. 

**input and output values** 
```{r}
frh <- dea(x,y,RTS = "add")
```

**calculate efficiency and name the column**
```{r}
eff_frh<- as.data.frame(frh$eff)
colnames(eff_frh)<- c("efficiency_frh")
eff_frh
```
According to the above efficiency values, \(DMU_6\) is inefficient because its' efficient value is below 1 and all the other DMUs are identified as efficient under the assumption of FRH.


**Find the peers**
```{r}
peer_frh<-peers(frh)
peer_frh
```
According to the above peer identification, all the DMUs except \(DMU_6\) become their own peers and only \(DMU_6\) consider \(DMU_2\) as its' peer. Therefore \(DMU_6\) seems to be inefficient. 

**Find the lambdas**
```{r}
lambda_frh <- lambda(frh)
lambda_frh
```
These lambda values are exactly same as the lambda values of FDH. 
Facility 1,2,3,4 and 5 are 100% efficient, and its efficiency score is calculated by comparing it to itself.Facility 6 is less efficient than the other facilities, and its efficiency score is calculated by comparing it to Facility 2. This means that Facility 6 could improve its efficiency by using its inputs and outputs more efficiently, or by finding ways to reduce its inputs or increase its outputs.

**Tabular data for FRH**
```{r}
tabular_frh <- cbind(peer_frh,lambda_frh,eff_frh)
tabular_frh
```
According to the tabular data of FRH, \(DMU_6\) is inefficient and it can reduce its' inefficiency from learning its peer of \(DMU_2(L2)\). 

**Plot the result**
```{r}
dea.plot(x,y,RTS = "add", ORIENTATION = "in-out", txt = TRUE, main= "Free Replicability Hull (FRH) Graph")
```

# Summary

According to the DEA analysis under all DEA assumptions of FDH, CRS, VRS,IRS, DRS, and FRH all the inefficient DMUs can be summarize as follow. So Under all the assumptions \(DMU_6\) is identified as inefficient. Under four assumptions \(DMU_5\) is identified as inefficient. As well as DMU_3 is inefficient according to CRS and IRS assumptions. 
```{r}

df2 <- data.frame(
  FDH = c("DMU_6", " ", " "),
  CRS = c("DMU_3", "DMU_5", "DMU_6"), 
  VRS = c("DMU_5", "DMU_6", " "),
  IRS = c("DMU_3", "DMU_5", "DMU_6"),
  DRS = c("DMU_5", "DMU_6", " "),
  FRH = c("DMU_6"," ", " ")
)
df2
```

